Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
More wording
Improve Problem -> Hspec

\noindent Though the code block itself is a useful feature,
we think this kind of usage has problems.
If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.

@@

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Spec
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      assertEqual "" [3, 2, 1]
                     (reverse [1 :: Int, 2, 3])

@@

\noindent The {\tt it} function combines a text description for a
behavior and a property or an example that gives some confidence in
that behavior into a spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

The \texttt{describe} function combines a list of specs into a larger spec.
%% It can be used to organize a spec as a tree.
%% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all properties and examples are evaluated, and failing properties
and examples are reported to the developer.

>>>>

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.
If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.

@@

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
main :: IO ()
main = spec $ do
  describe "reverse" $ do
    it "reverses a list" $
      assertEqual "" [3, 2, 1] (reverse [1, 2, 3])

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence into a spec.
Code examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

The \texttt{describe} function combines a list of specs into a larger spec.
%% It can be used to organize a spec as a tree.
%% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested, and behavior with evidence that does not
hold is reported to the developer.
